### 2020-01-21 paper/results.tex
Minor changes from Andrei

The control rod parameters including control rod worth (CRW), interference 
between CR clusters, and integral and differential control rod worths are 
described in this part. 
Table~\ref{tab:worth} shows calculated control rod worth, the amplification 
factor (A$_{CRi}$), and the type of interference for the six different 
absorbers.

@@

Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with the six 
different absorbing materials. The results show that all absorbing materials 
have almost the same integral rod worth in the upper half of the core 
($<250$ cm from the upper boundary of the core). Further insertion of the 
control rods shows the unique absorption characteristics of each material (see 
part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
Gd$_2$O$_3$, which has the lowest absorption ability among the other absorbing 
materials in this study. Notably, all results are based on steady state calculations.

>>>>

The control rod parameters including control rod worth (CRW), interference 
between CR clusters, and integral and differential control rod worths are 
described in this part. 
Table~\ref{tab:worth} shows calculated control rod worth, the amplification 
factor (A$_{CRi}$), and the type of interference for six different 
absorbers.

@@

Figure~\ref{fig:CSD} shows the integral CRW for only CSD clusters with six 
different absorbing materials. The results show that all absorbing materials 
have almost the same integral rod worth in the upper half of the core 
($<250$ cm from the upper boundary of the core). Further insertion of the 
control rods shows the unique absorption characteristics of each material (see 
part~\ref{CR_worth}). B$_4$C-90 absorbs much more neutrons than the 
Gd$_2$O$_3$, which has the lowest absorption ability among the other absorbing 
materials in this study. Notably, all results are based on steady state calculations.
